Diagnoses and cell types

### 2025-10-08 analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd
phrasing

There are five library with an order of magnitude more  7x as many reference as query cells; let's look more closely at the validation groups present to get a sense.

>>>>

There are five library with an order of magnitude more reference than query cells; let's look more closely at the validation groups present to get a sense.
